Experience Report: Kandria - A Game in Common Lisp

### 2023-02-11 els2023-kandria/paper.tex
Minor

Newly developed tools to better visualise the data gathered by the statistical profiler, such as the ``flamegraph'' visualiser developed by Jan Moringe have also been invaluable in gaining a better understanding of the performance characteristics of the code.

@@

\section{Acknowledgements}\label{acknowledgements}
We would like to thank \textit{you} for being beautiful and nice :)

>>>>

Newly developed tools to better visualise the data gathered by the statistical profiler, such as the ``flamegraph'' visualiser developed by Jan Moringen have also been invaluable in gaining a better understanding of the performance characteristics of the code.

@@

\section{Acknowledgements}\label{acknowledgements}
We would like to thank the various contributors to all of the projects that have made it possible to make Kandria in the first place, and we would like to thank \textit{you} for being beautiful and nice.
